---
title: "dplyr filter homework"
author: "Your Name"
date: "2019-03-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Exercises

Loading required libraries:
```{r}
library(tidyverse)
library(here)
```

Importing dataset:
```{r}
viruses <- read_csv(here("data", "viruses.csv"))
```

Print out dataset:
```{r}
viruses
```


1. Find all viruses that:

- have genome of over 10000kb

```{r}
filter(viruses, size_kb >= 10000)
```

- belong to *Papillomaviridae*

```{r}
filter(viruses, subgroup == "Papillomaviridae")
```

- are from plants and environment

```{r}
filter(viruses, host == "plants" | host == "environment")
```

- were released between 01. January 1980 - 01. January 1990, including these days:

```{r}
library(lubridate)
date1 <- dmy("01.01.1980")
date2 <- dmy("01.01.1990")
filter(viruses,release_date >= date1 & release_date <= date2)
```

2. there is also between() function in dplyr. 

What does it do? Run ?between
```{r}
library(lubridate)
#?between
filter(viruses,between(release_date,dmy("01.01.1980"), dmy("01.01.1990")))
```


How can you use it to find viruses with genomes between 1 to 2 kb?

```{r}
filter(viruses,size_kb >= 1 & size_kb <= 2)
```

3. Find Enteroviruses:

Hint: use str_detect()
```{r}
filter(viruses,str_detect(organism_name, ".*nterovirus"))
```

